Honors Thesis

### 2009-02-27 honors_thesis/paper.tex
Working on proposal

\section{Methodology}

The methodology of this research will procede as follows:

Compare to original How to control for external factors (nice in CS, though not
in other sciences) Once you've run experiments, what are you looking for?
Anything you can say about what code you're using, and how you intend to
compare results.  People are concerned about how you're going to draw
conclusions.  It matters what kind of statistical tests you are going to do.
We're going to run a number of trials because it's a randomized algorithm.
Test against multiple functions, with multiple topologies - some synthetic
functions, and some real-world applications.  Run with standard constriction
coefficient.  How do you compare your results to things other people have done?

\begin{itemize}

\item

\end{itemize}

@@

>>>>

\section{Procedures}

The bulk of the work for this project will be writing code and running
experiments.  Research has been done to see what has been done in the field, to
know what the results need to be compared to.  In implementing speculative
execution, care will be taken that the algorithm behaves exactly like the
original, standard particle swarm optimization (PSO) algorithm in every aspect
except the speed-up.  The same constants will be used as are commonly published
in the literature.

In running experiments, many trials will be run and averaged, as there is a
random component in this algorithm.  Statistics will be used for all
comparisons to the original PSO algorithm.  The success criterion will be a
better performance of the algorithm as measured by the lowest function
evaluation seen over a number of iterations for several benchmark and
real-world problems.  Speculative execution takes more work than regular PSO
with the same number of particles, so the two algorithms will be compared at
points where they use equal amounts of processing power.

@@

\begin{enumerate}
\item Introduction
\item Related Work
\item Particle Swarm Optimization
\item Speculative Execution
\item Speculative Execution in PSO
\item Experiments
\item Results and Conclusions
\item Future Work
\item References
\end{enumerate}
